---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### **This tutorial demonstrate the usage of the function in hw3.625 package**

To use the function `hw3_lm` in the package:

```{r}
library(hw3.625)
# Load the data containing the variables in the model
data("mtcars")
```

```{r}
# Fit the linear regression model
model_hw3 <- hw3_lm(mpg ~ wt + hp + cyl, data = mtcars)
print(model_hw3)
```

## **Comparison Against Original lm() Function**

### **Correctness**

In order to compare the correctness of my function, we also need to fit another linear regression model using the lm() function.
```{r}
# Fit another linear regression model using lm()
model_lm <- lm(mpg ~ wt + hp + cyl, data = mtcars)
summary(model_lm)
```

Check coefficients
```{r}
coef_hw3 <- model_hw3$coefficients[, "Estimate"]
coef_lm <- summary(model_lm)$coefficients[, "Estimate"]
all.equal(coef_hw3, coef_lm)
```

Check residuals
```{r}
resid_hw3 <- unname(model_hw3$residuals)
resid_lm <- unname(resid(model_lm))
all.equal(resid_hw3, resid_lm)
```

Check R-squared
```{r}
r2_hw3 <- model_hw3$m_r2
r2_lm <- summary(model_lm)$r.squared
all.equal(r2_hw3, r2_lm)
```

To verify the correctness of the `hw3_lm` function, we test only the coefficients, residuals, and multiple R-squared values. By using the `all.equal` function, we can ensure that the `hw3_lm` and `lm` functions generate the same linear regression model.

### **Efficiency**

```{r}
# Test the efficiency of lm() function
system.time({lm_model <- lm(mpg ~ wt + hp + cyl, data = mtcars)})

# Test the efficiency of hw3_lm() function
system.time({hw3_model <- hw3.625::hw3_lm(mpg ~ wt + hp + cyl, data = mtcars)})
```

To test whether `hw3_lm` is as efficient as `lm`, we compare their system times. Since both functions show similar elapsed times when fitting a linear regression model, we can conclude that their efficiency is comparable.
